Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-07-27 manuscript/manuscript.tex
addressing review comments [ci skip]

For those unfamiliar with Markov state modeling, ``\emph{Markov State Models: From an Art to a Science}''~\cite{msm-brooke} provides a recent overview, while ``\emph{Markov models of molecular kinetics: Generation and validation}''~\cite{msm-jhp} describes the basic MSM theory and methodology in detail. Two textbooks exist that focus on computational methods and applications~\cite{msm-book} and mathematical theory~\cite{schuette-sarich-book}.

@@

While the present tutorial covers Markov State Modeling 101, we encourage the user to explore other, more recent extensions of the methodology.
Multi-ensemble Markov models (MEMMs)~\cite{dtram,tram} can be used to combine unbiased and biased simulations so as to probe kinetics of very rare events~\cite{trammbar}; MEMMs are implemented in PyEMMA.
Recently, there have been steps towards replacing the traditional user-directed pipeline (involving featurizing, reducing dimension, discretizing, MSM estimation and coarse-graining) by a single end-to-end deep learning method such as VAMPnets~\cite{vampnet}.
Other deep learning methods for performing the dimension reduction~\cite{tae}, finding reaction coordinates for enhanced sampling~\cite{hernandez-vde,Sultan2018-vde-enhanced-sampling,Ribeiro2018-rave}, and generative MSMs~\cite{deep-gen-msm-preprint} have been put forward and are likely to spawn an active field of research on its own right.
Implementations of some of these methods are available or is under development in the package deeptime \url{github.com/markovmodel/deeptime}.

>>>>

For those unfamiliar with Markov state modeling, ``\emph{Markov State Models: From an Art to a Science}''~\cite{msm-brooke} provides a recent overview, while ``\emph{Markov models of molecular kinetics: Generation and validation}''~\cite{msm-jhp} describes the basic MSM theory and methodology in detail. Additionally, two textbooks exist that focus on computational methods and applications~\cite{msm-book} and mathematical theory~\cite{schuette-sarich-book}.

@@

While the present tutorial is intended to cover Markov State Modeling 101, we encourage the user to explore other, more recent extensions of the methodology.
Multi-ensemble Markov models (MEMMs)~\cite{dtram,tram} can be used to combine unbiased and biased simulations so as to probe kinetics of very rare events~\cite{trammbar}; MEMMs are implemented in PyEMMA.
Recently, there have been steps towards replacing the traditional user-directed pipeline (involving featurizing, reducing dimension, discretizing, MSM estimation and coarse-graining) by a single end-to-end deep learning method such as VAMPnets~\cite{vampnet}.
Other deep learning methods for performing the dimension reduction~\cite{tae}, finding reaction coordinates for enhanced sampling~\cite{hernandez-vde,Sultan2018-vde-enhanced-sampling,Ribeiro2018-rave}, and generative MSMs~\cite{deep-gen-msm-preprint} have been put forward and are likely to spawn an active field of research on its own right.
Implementations of some of these methods are available or are under development in the deeptime package \url{github.com/markovmodel/deeptime}.
